Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
Updated scenario

@@

Two vectors for infiltrating an origin has been identified, via syntax 
injection, or content smuggling.

>>>>

Other potential targets for this scenario are job broker services and conference 
submission systems, which by design allow submission of PDFs to be viewed by
users.

@@

In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more than one way
This paper identifies two vectors for infiltrating an origin, via syntax 
injection, or content smuggling.
